cardinalR: Generating interesting high-dimensional data structures

### 2025-04-30 paper-cardinalR.Rmd
Add Figure title for Figure1

<!-- 1) Generate a data structure with different shapes (two non-linear, one gaussian, one linear, one cone in 5-D simplex) and fit different NLDR (Then, demonstrate how this data can be used to assess the ability of different dimensionality reduction techniques (e.g., PCA, t-SNE, UMAP) to preserve the underlying structure in a lower-dimensional embedding.) -->

<!-- 2) Add noise dimensions to the same data by linking two or three clusters, then discuss how single and complete linkage affect for the solutions (refer Di's book <https://dicook.github.io/mulgar_book/8-hierarchical.html>) -->

@@

```{r, label = "fig-highd-proj", fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `mobiusgau` data."}
#| fig-width: 15
#| fig-height: 5
five_clusts_proj1 + five_clusts_proj2 + five_clusts_proj3 +
  plot_layout(ncol = 3, guides = "collect") 
```

>>>>

@@

```{r, label = "fig-highd-proj", fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `mobiusgau` data. The helical spiral cluster is represented in dark green, the hemisphere cluster in orange, the uniform cube-shaped cluster in purple, the blunted cone cluster in pink, and the Gaussian-shaped cluster in light green."}
#| fig-width: 15
#| fig-height: 5

five_clusts_proj1 + five_clusts_proj2 + five_clusts_proj3 +
  plot_layout(ncol = 3, guides = "collect") 
```
